```r
---
title: "Unique Pizza Ingredients"
author: "Los optimizados"
date: "`r Sys.Date()`"
output: html_document
---

Setup chunk

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Extracting Unique Ingredients

Read the dataset and list all the unique ingredients from the `pizza_ingredients` column.

### Load Required Libraries
```{r libraries}
required_packages <- c("readxl", "dplyr", "stringr", "tidyr")

install_if_missing <- function(packages) {
  missing_packages <-
    packages[!(packages %in% installed.packages()[, "Package"])]
  if (length(missing_packages) > 0) {
    install.packages(missing_packages)
  }
}

install_if_missing(required_packages)
library(readxl)
library(dplyr)
library(stringr)
library(tidyr)
```

### Read the Dataset
```{r read-data}
file_path <- "src/creation_new_dataset/pizza_sales.xlsx"

pizza_data <- read_excel(file_path)

head(pizza_data)
```

### Extract and List Unique Ingredients
```{r extract-ingredients}
ingredients_list <- pizza_data %>%
  pull(pizza_ingredients) %>%
  str_split(", ") %>%
  unlist()

unique_ingredients <- unique(ingredients_list) %>%
  sort()

cat("Total unique ingredients:", length(unique_ingredients), "\n")

unique_ingredients
```