Certainly! Below is an example of an RMarkdown file that reads the `pizza_ingredients` column from the *Data Model - Pizza Sales.xlsx* file, extracts all unique ingredients, and lists them.

```r
---
title: "Unique Pizza Ingredients"
author: "Your Name"
date: "`r Sys.Date()`"
output: html_document
---

Setup chunk

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Extracting Unique Ingredients

We will read the dataset and list all the unique ingredients from the `pizza_ingredients` column.

### Load Required Libraries
```{r libraries}
# List of required packages
required_packages <- c("readxl", "dplyr", "stringr", "tidyr")

# Function to check and install missing packages
install_if_missing <- function(packages) {
  missing_packages <-
    packages[!(packages %in% installed.packages()[, "Package"])]
  if (length(missing_packages) > 0) {
    install.packages(missing_packages)
  }
}

# Install missing packages
install_if_missing(required_packages)
library(readxl)   # To read Excel files
library(dplyr)    # For data manipulation
library(stringr)  # For string operations
library(tidyr)    # For data tidying
```

### Read the Dataset
```{r read-data}
# Specify the file path
file_path <- "src/creation_new_dataset/pizza_sales.xlsx"

# Read the dataset
pizza_data <- read_excel(file_path)

# Display the first few rows of the dataset
head(pizza_data)
```

### Extract and List Unique Ingredients
```{r extract-ingredients}
# Extract the 'pizza_ingredients' column and split the ingredients
ingredients_list <- pizza_data %>%
  pull(pizza_ingredients) %>%  # Extract the column
  str_split(", ") %>%          # Split by ", "
  unlist()                     # Flatten the list into a vector

# Get unique ingredients
unique_ingredients <- unique(ingredients_list) %>%
  sort()  # Sort alphabetically

# Display the number of unique ingredients
cat("Total unique ingredients:", length(unique_ingredients), "\n")

# Print the list of unique ingredients
unique_ingredients
```